---
title: "HW 1"
author: "Kristina Howell"
date: "9/13/2020"
output: html_document
---

### Question 1

The following code creates a dataframe (titled df_1) consisting of a numeric vector, a logic vector, a character vector, and a three level factor vector. The contents of the dataframe are displayed after.

``` {r setup, message = FALSE}
library(tidyverse)
```

``` {r dataframe_generation}
df_1 = 
  tibble(
       vec_rand = rnorm(10),
       vec_logic = vec_rand > 0,
       vec_char = c("A", "B", "C", "D", "E", 
                    "F", "G", "H", "I", "J"),
       vec_factor = factor(c("mild","mild","mild","mild",
                             "moderate", "moderate", "moderate",
                             "severe", "severe", "severe"))
  )

df_1
```

The following code attempts to take the mean of each vector. It displays two possible ways to code the calculation of a vec_rand.

```{r calculation_of_mean}
mean(pull(df_1,vec_rand)) 

mean(df_1$vec_rand)
mean(df_1$vec_logic)
mean(df_1$vec_char)
mean(df_1$vec_factor)
```

The mean is calculated for the random sample vector (vec_rand) and the logic vector (vec_logic). The code produces an error for the character vector (vec_char) and the factor vector (vec_factor).

The following code chunk applies the as.numeric function to the logical, character, and factor variables. The output is omitted.

```{r as.numeric_function, results = 'hide', warning = FALSE}
as.numeric(df_1$vec_logic)
as.numeric(df_1$vec_char)
as.numeric(df_1$vec_factor)
```

The output computes the vectors into numeric functions. For example, the logic vector changes to 0 and 1 based on the true/ false status of each entry. The character vector outputs all NA. The factor vector changes each level to 1, 2, and 3, respectively. These changes allow R to then perform calculations on the vectors as if they were numeric functions. 

The following code chunk performs various procedures, as outlined in the comments.
```{r manipulation_of_vectors}
#Convert the logical vector to numeric and multiply the random sample by the result.
as.numeric(df_1$vec_logic)*(df_1$vec_rand)

#Convert the logical vector to a factor and multiply the random sample by the result.

#convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```


### Question 2

Load the penguins dataset:

```{r load_dataset_package}
data("penguins", package = "palmerpenguins")
```

The penguin dataset includes the variables: `r names(penguins)`. The dataset variables addresses demographic and individual aspects of the penguins examined. The penguins dataset consists of `r nrow(penguins)` rows and `r ncol(penguins)` columns. The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`.

The following code creates a scatterplot comparing bill length in mm to flipper length in mm by species. 

```{r create_scatterplot}
ggplot(penguins, aes(x = bill_length_mm, 
                     y = flipper_length_mm, 
                     color = species)) + geom_point()

ggsave(filename = "bill_flipper.pdf",
       plot = last_plot())
```


